---
title: "DataFest - PiazzzzaHut"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(tidyverse) # Modern data science library 
library(plm)       # Panel data analysis library
library(tseries)   # For timeseries analysis
library(lmtest)    # For hetoroskedasticity analysis
library(tidyr)
library(REEMtree)
library(rpart)
library(maptree)
library(TH.data)
```

# General Trend Graph

```{r}
covid <- read_csv("Data/daily.csv")
covid_us <- read_csv("Data/us.csv")
head(covid, 10)
head(covid_us, 10)
```
<br>
Confirmed and deaths cases in US states (data end in 6/4)
<br>
```{r}
data = covid 

p1 <- ggplot(data, aes(x=date)) +
  geom_line(aes(y=log(positive), color='Confirmed'))+ 
  geom_line(aes(y=log(death), color='Deaths')) +
xlab('From Jan to June') + ylab('Count') +
theme(legend.title=element_blank(), axis.text.x = element_text(angle=45, hjust=1)) +
scale_color_manual(values = c('Confirmed' = 'brown',
'Deaths' = 'black')) + facet_wrap(~state)

plot1 <- p1 + labs(title=paste0('Number of Cases - 2020.06.04'))
plot1
```
<br>
Confirmed and deaths cases in US (data end in 6/4)
<br>
```{r}
p2 <- ggplot(covid_us, aes(x=date)) +
  geom_line(aes(y=cases, color='Confirmed'))+ 
  geom_line(aes(y=deaths, color='Deaths')) +
xlab('') + ylab('Count') +
theme(legend.title=element_blank(), axis.text.x = element_text(angle=45, hjust=1)) +
scale_color_manual(values = c('Confirmed' = 'brown',
'Deaths' = 'black'))

plot2 <- p2 + labs(title=paste0('Number of Cases - 2020.06.04'))
plot2
```

# OLS/Fixed Effect/Random Effect Model for Panel Data

```{r}
mydata <- read.csv("Data/datafest_final_data.csv")
mydata <- na.omit(mydata)
head(mydata, 10)

# Set data as panel data
pdata <- pdata.frame(mydata, index=c("date","state"))
f <- change_infection~stay_at_home_order+mask_mandates+travel_restrictions+restaurant_limit
```
<br>
We can use plm to run a straightforward OLS regression on the entire panel, which is usually called a "pooled" model (all the years are pooled into a big data set and treated as separate observations). 
<br>
```{r}
# Pooled OLS estimator
pooling <- plm(f, data=pdata, model= "pooling")
summary(pooling)
```

```{r}
# Between estimator
between <- plm(f, data=pdata, model= "between")
summary(between)

# First differences estimator
firstdiff <- plm(f, data=pdata, model= "fd")
summary(firstdiff)
```

```{r}
# Fixed effects or within estimator
fixed <- plm(f, data=pdata,index=c("date","state"), model= "within")
summary(fixed)
```
<br>
Since the p-value >0.05, fixed model is not suitable for parameters estimation.
<br>
```{r}
#Random effects estimator
random <- plm(f, data=pdata, index=c("date","state"),model= "random")
summary(random)
```
<br>
Model selection and comparison 
<br>
```{r}
# LM test for random effects versus OLS
plmtest(pooling,type=c("bp"))
```

# Decision Tree Learning for Panel Data

```{r}
fit <- rpart(f, method='anova', data=mydata)
printcp(fit)
pfit <- prune(fit,cp= fit$cptable[which.min(fit$cptable[,"xerror"]), "CP"])
draw.tree(pfit)
```












